---
title: 'House prices: Lasso, XGBoost, and a detailed EDA'
output: html_document
---
##Data From https://www.kaggle.com/erikbruin/house-prices-lasso-xgboost-and-a-detailed-eda/data
#Read data
```{r}
sample_submission = read.csv("./house_price_data/sample_submission.csv")
test <- read.csv("./house_price_data/test.csv")
train = read.csv("./house_price_data/train.csv")


```
#load packages
```{r}
library(ggplot2)
library(ggrepel)
library(knitr)
library(dplyr)
library(plyr)
library(caret)
library(gridExtra)
library(scales)
library(Rmisc)
library(randomForest)
library(psych)
library(xgboost)

```

#The response variable; SalePrice
##As you can see, the sale prices are right skewed. This was expected as few people can afford very expensive houses.

```{r}
test_labels <- test$Id
test$Id <- NULL
train$Id <- NULL
test$SalePrice <- NA
all <- rbind(train, test)

ggplot(data=all[!is.na(all$SalePrice),], aes(x=SalePrice)) +
  geom_histogram(fill="blue", binwidth = 10000) +
  scale_x_continuous(breaks= seq(0, 800000, by=100000))

```

#The most important numeric predictors
##The character variables need some work before using them. 
##To see which numeric variables have a high correlation with the SalePrice.
###We can see OverallQual has the highest correlation with the SalePrice.

```{r}
numericVars <- which(sapply(all, is.numeric)) #index vector numeric variables
numericVarNames <- names(numericVars) #saving names vector for use later on
cat('There are', length(numericVars), 'numeric variables')
## There are 37 numeric variables
all_numVar <- all[, numericVars]
cor_numVar <- cor(all_numVar, use="pairwise.complete.obs") #correlations of all numeric variables

#sort on decreasing correlations with SalePrice
cor_sorted <- as.matrix(sort(cor_numVar[,'SalePrice'], decreasing = TRUE))
#select only high corelations
CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.5)))
cor_numVar <- cor_numVar[CorHigh, CorHigh]
library(corrplot)
corrplot.mixed(cor_numVar, tl.col="black", tl.pos = "lt")

```

#Overall Quality
##Overall Quality rates the overall material and finish of the house on a scale from 1 (very poor) to 10 (very excellent).
###Conclusion:Expensive houses have better overall quallities.
```{r}
ggplot(data=all[!is.na(all$SalePrice),], aes(x=factor(OverallQual), y=SalePrice))+
  geom_boxplot(col='blue') + labs(x='Overall Quality') +
  scale_y_continuous(breaks= seq(0, 800000, by=100000))

```

#Above Grade (Ground) Living Area (square feet)
##The numeric variable with the second highest correlation with SalesPrice is the Above Grade Living Area. This make a lot of sense; big houses are generally more expensive.
###Conclusion:There are correlations between SalesPrice and locations.
```{r}
ggplot(data=all[!is.na(all$SalePrice),], aes(x=GrLivArea, y=SalePrice))+
  geom_point(col='blue') + geom_smooth(method = "lm", se=FALSE, color="black", aes(group=1)) +
  scale_y_continuous(breaks= seq(0, 800000, by=100000)) +
  geom_text_repel(aes(label = ifelse(all$GrLivArea[!is.na(all$SalePrice)]>4500, rownames(all), '')))


```

```{r}
all[c(524, 1299), c('SalePrice', 'GrLivArea', 'OverallQual')]
```

```{r}
##      SalePrice GrLivArea OverallQual
## 524     184750      4676          10
## 1299    160000      5642          10
```

```{r}
NAcol <- which(colSums(is.na(all)) > 0)
sort(colSums(sapply(all[NAcol], is.na)), decreasing = TRUE)
```

```{r}
##       PoolQC  MiscFeature        Alley        Fence    SalePrice 
##         2909         2814         2721         2348         1459 
##  FireplaceQu  LotFrontage  GarageYrBlt GarageFinish   GarageQual 
##         1420          486          159          159          159 
##   GarageCond   GarageType     BsmtCond BsmtExposure     BsmtQual 
##          159          157           82           82           81 
## BsmtFinType2 BsmtFinType1   MasVnrType   MasVnrArea     MSZoning 
##           80           79           24           23            4 
##    Utilities BsmtFullBath BsmtHalfBath   Functional  Exterior1st 
##            2            2            2            2            1 
##  Exterior2nd   BsmtFinSF1   BsmtFinSF2    BsmtUnfSF  TotalBsmtSF 
##            1            1            1            1            1 
##   Electrical  KitchenQual   GarageCars   GarageArea     SaleType 
##            1            1            1            1            1
```

```{r}
cat('There are', length(NAcol), 'columns with missing values')
```

```{r}
## There are 35 columns with missing values
```

##學習筆記
###要記得library才不會畫不出圖